European or American? A re-examination of the transatlantic influence over the IMF

### 2025-09-12 manuscript/manuscript.qmd
future research: 3rd

Third, examining variation in influence across different types of IMF programmes—such as Stand-By Arrangements, Extended Fund Facilities, or newer instruments like the Flexible Credit Line—could reveal whether European and American influence operates differently depending on the specific lending modality or the severity of the borrower's economic difficulties.

Finally, our findings suggest the value of disaggregating "Western" influence in studies of other international organisations. The World Bank, regional development banks, and newer institutions like the Asian Infrastructure Investment Bank may exhibit similar asymmetries in great power influence that are masked by treating Western actors as a unified bloc.

>>>>

Finally, our findings suggest the value of applying a similar disaggregation of Western influence to other international organisations. Beyond the World Bank, promising candidates include the OECD, the Bank for International Settlements (BIS), the WTO, and the European Bank for Reconstruction and Development (EBRD). Each involves overlapping Western leadership but potentially divergent US and European priorities, offering a fertile testing ground for whether the asymmetries we document are specific to the IMF or reflect broader patterns of transatlantic governance.
